\documentclass{letter}
\usepackage{fancyhdr}
\fancypagestyle{plain}{
\fancyhf{}
\fancyhead[C]{Statement of Purpose}
\fancyfoot[C]{Stephen Edmans}
}
\pagestyle{plain}
\begin{document}
Passionate about learning new things, in some ways it does not matter what, but if it is a choice between something computer related, or mathematics related, and anything else then the former usually wins out. As an example I am currently learning to fly and I am studying for a graduate diploma in mathematics.
\par
Didn't get higher education at the usual age.
\par
Spent years working away from home (go to work on Monday, return home on Friday)
\par
I got a job where I was working close to home and I took a course at Birkbeck College, University of London. This is a college that styles itself as London's evening university. I really enjoyed this class and my employer was happy to guarantee that I would be based in central london for the duration of a degree course.  Birkbeck college has a masters degree program where previous work experience can be used an entry criteria, instead of a batchelors degree. One of the introductory lecture I attended was on study skills. A part of this lecture talked about research, and research skills, it was during this part of the lecture that I realised that the part of my job that I enjoyed the most was research. 
\par
I have always been the person to go to with difficult ``how do I do this'' type questions and I get a great deal of pleasure from helping people understand what they are trying to accomplish.
\par
After I started this course, and I was able to demonstrate my abilities, and I managed to transfer into the much more specific course that I graduated from.
\par
There are a few areas of research that I am fascinated by, these are distributed systems, programming languages and paradigms and database systems.
\par
I have been heavily involved with big data and graph databases at work for the past couple of years and there are a few issues that I have seen with them that I would like to research. My initial thoughts are that I would like to work on a distributed graph database, what is the best way to distribute the vertices around the cluster, what is the best way to distribute the edges around the cluster, what is the best data structure to store vertices and edges, is the same data structure best for both memory and disk storage, what is the best way for a client application to communicate with the cluster, there are two major types of relational databases OLTP and OLAP, is there an equivalence to OLAP for graph databases; how mature are the authorisation techniques for graph databases, can we learn something from relational databases; another function that relational databases provide are triggers, is there some way we can, or should, include these with graph databases.
\par
At the present moment I am in two minds as to what I want to do once I have obtained a Phd, one part of me wants to concentrate research, whereas the other part of me is interested in teaching.
\end{document}